### 2018-09-20 Latex/section_wave_cascade_f=0.tex
Include combined figure in latex

\begin{figure}
\centerline{\includegraphics[width=3.15in]{../Pyfig/fig_spect_energy_budg_c=100_N=3840}}
\caption{Spectral energy fluxes averaged over a long simulation for $c
= 100$ and $n = 3840$.  The fluxes are nondimensionalized by $\eps$
and plotted versus $k/k_f$.  }
\label{fig_seb}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=3.15in]{../Pyfig/fig_Kolmo_c=20_N=3840}}
\caption{
Third order structure functions involved in the exact Kolmogorov law (\ref{eq_Kolmo})
averaged over a long simulation for $c = 20$ and $n = 3840$.
%
The structure functions are normalized by $4 \eps r$.
%
Black thick line, $\mean{ \delta J_L|\delta \uu|^2 }
+ c^2\mean{\delta u_L(\delta h)^2}$;
light thin line, $c^2\mean{\delta u_L (\delta h)^2}$;
dark thin line, $\mean{\delta J_L |\delta \uu|^2}$.
%
The dotted straight line shows $4 \eps_q r$,
where $\eps_q$ is the quadratic energy dissipation rate.
}
\label{fig_Kolmo}
\end{figure}

Figure~\ref{fig_Kolmo} shows the quantity $\mean{\delta J_L|\delta
\uu|^2 } + c^2\mean{\delta u_L(\delta h)^2 }$ (black thick line)
normalized by $4 \eps r$ for $c = 20$ and $n = 1920$.
%
In this section, the brackets $\mean{}$ denote the average over space
and time.
%
The dotted straight line shows the quantity $4 \eps_q r$, where
$\eps_q$ is the quadratic energy dissipation rate (see
appendix~\ref{app_comp}) which takes place at small scales.
%
We see that the Kolmogorov law (\ref{eq_Kolmo}) is well satisfied
between \Add{$r \simeq 0.02L_f$ and $r \simeq 0.1 L_f$}.  The dark and
light thin continuous lines correspond to the quantities $\mean{\delta
J_L|\delta \uu|^2 }$ and $c^2\mean{\delta u_L(\delta h)^2}$,
respectively.
%
These two quantities are nearly equal over the inertial and
dissipation ranges, which is consistent with a wave cascade when
$f=0$.
%
The agreement with the Kolmogorov law and the equality between
$\mean{\delta J_L|\delta \uu|^2 }$ and $c^2\mean{\delta u_L(\delta
h)^2}$ are the equivalents in the separation space of the plateau in
the total energy flux and the equality between $\Pi_K$ and $\Pi_A$,
respectively.

>>>>

\begin{figure}
\centerline{\includegraphics[width=\linewidth]{../Pyfig/fig_flux_struct_combined}}
\caption{(Left) Spectral energy fluxes averaged over a long simulation for $c
= 100$ and $n = 3840$.  The fluxes are nondimensionalized by $\eps$
and plotted versus $k/k_f$.
(Right)
Third order structure functions involved in the exact Kolmogorov law (\ref{eq_Kolmo})
averaged over a long simulation for $c = 20$ and $n = 3840$.
%
The structure functions are normalized by $4 \eps_q r$.
%
Black thick line, $\mean{ \delta J_L|\delta \uu|^2 }
+ c^2\mean{\delta u_L(\delta h)^2}$;
light thin line, $c^2\mean{\delta u_L (\delta h)^2}$;
dark thin line, $\mean{\delta J_L |\delta \uu|^2}$.
%
The dotted straight line shows $4 \eps_q r$,
where $\eps_q$ is the quadratic energy dissipation rate.
}
\label{fig_seb}
\end{figure}

@@

Figure~\ref{fig_seb} also shows the quantity $\mean{\delta J_L|\delta
\uu|^2 } + c^2\mean{\delta u_L(\delta h)^2 }$ (black thick line)
normalized by $4 \eps r$ for $c = 20$ and $n = 1920$.
%
In this section, the brackets $\mean{}$ denote the average over space
and time.
%
The dotted straight line shows the quantity $4 \eps_q r$, where
$\eps_q$ is the quadratic energy dissipation rate (see
appendix~\ref{app_comp}) which takes place at small scales.
%
We see that the Kolmogorov law (\ref{eq_Kolmo}) is well satisfied
between \Add{$r \simeq 0.02L_f$ and $r \simeq 0.1 L_f$}.  The dark and
light thin continuous lines correspond to the quantities $\mean{\delta
J_L|\delta \uu|^2 }$ and $c^2\mean{\delta u_L(\delta h)^2}$,
respectively.
%
These two quantities are nearly equal over the inertial and
dissipation ranges, which is consistent with a wave cascade when
$f=0$.
%
The agreement with the Kolmogorov law and the equality between
$\mean{\delta J_L|\delta \uu|^2 }$ and $c^2\mean{\delta u_L(\delta
h)^2}$ are the equivalents in the separation space of the plateau in
the total energy flux and the equality between $\Pi_K$ and $\Pi_A$,
respectively.
